---
title: "DDP-Week4 Project-Slides"
author: "Santosh Pawar"
date: "December 17, 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

##Introduction

The Google Maps Geocode Tool can be used to query latitude and longtitude coordinates of places of interest. The tool uses the Google Maps API service for latidue and longtitude coordnate information and the Shiny Package for UI creation.
The main function that queries Google Maps API for latitude and longtitude information is the geoCode function. This function takes in the search criteria and returns the latitude, longtitude, type of location and address identified.

##Advantages and Limitations
######Advantages
    - Users don't need to know Google Maps API and R
    - Point locations of places in terms of Latitude and Longtitude coordinates
    - Available for free from Google Maps API

####Limitations
    - Only a maximum of 10 addresses can be queried at one time 

#####Example of geocode R Output
```{r Geocode, echo = TRUE}
library(RCurl)
library(RJSONIO)
library(plyr)
 url <- function(address, return.call = "json", sensor = "false") {
 root <- "http://maps.google.com/maps/api/geocode/"
 u <- paste(root, return.call, "?address=", address, "&sensor=", sensor, sep = "")
 return(URLencode(u))}
```

##Example of geocode R output
#####Example of geocode R Output (contd..)
```{r Geocode2, echo = TRUE} 
geoCode <- function(address,verbose=FALSE) {if(verbose) cat(address,"\n")
u <- url(address)
doc <- getURL(u)
x <- fromJSON(doc,simplify = FALSE)
if(x$status=="OK") {lat <- x$results[[1]]$geometry$location$lat
lng <- x$results[[1]]$geometry$location$lng
location_type <- x$results[[1]]$geometry$location_type
formatted_address <- x$results[[1]]$formatted_address
return(c(lat, lng, location_type, formatted_address))} else {return(c(NA,NA,NA, NA))}}
address <- geoCode("Orlando, FL")
#Results presented as "Latitude","Longtitude","Location Type", "Mapped Address"
address
```

##References

This project's work is based on guidance from following sources.

    https://gist.github.com/josecarlosgonz/6417633#file-googlemapsandr-md
    http://www.r-bloggers.com/using-google-maps-api-and-r/



